```{r report-section-setup, include=FALSE}
estimate <- fit$estimate[1L, , drop = FALSE]
confidence_level <- 100 * (1 - fit$settings$alpha)
analysis_call <- paste(deparse(fit$call, width.cutoff = 500L), collapse = " ")
section_level <- if (multiple_analyses) 3L else 2L
section_heading <- function(text) {
  paste0(paste(rep("#", section_level), collapse = ""), " ", text)
}
```

`r if (multiple_analyses) paste0("## ", analysis_name) else ""`

<div class="eventsurvey-call">`r analysis_call`</div>

`r section_heading("Main result")`

The estimated window-average event effect is
**`r format_number(estimate$effect)`**. The honest
`r format_number(confidence_level, 0)`% confidence interval is
**[`r format_number(estimate$conf_low)`,
`r format_number(estimate$conf_high)`]**. Effects are expressed in the original
units of **`r fit$settings$outcome`**.

```{r main-result}
main_result <- data.frame(
  Quantity = c(
    "Average effect",
    "Standard error",
    "Conventional interval",
    "Bias bound",
    "Honest interval",
    "Reference windows",
    "Reference forecasts"
  ),
  Value = c(
    format_number(estimate$effect),
    format_number(estimate$std_error),
    paste0(
      "[", format_number(estimate$conventional_low), ", ",
      format_number(estimate$conventional_high), "]"
    ),
    format_number(estimate$bias_bound),
    paste0(
      "[", format_number(estimate$conf_low), ", ",
      format_number(estimate$conf_high), "]"
    ),
    estimate$n_windows,
    estimate$n_reference
  ),
  check.names = FALSE
)
knitr::kable(main_result, align = c("l", "r"))
```

`r section_heading("Automatic diagnostics")`

These checks describe features that may deserve attention. A “Review” status
does not invalidate the analysis and does not change any estimate. Review is
triggered by missing calendar periods, any observed period with fewer than 10
responses, pooled variance substitution, fewer than five rolling reference
windows, or an observed-period window spanning more calendar time than
requested.

```{r automatic-diagnostics}
diagnostic_table <- fit$diagnostics
names(diagnostic_table) <- c("Check", "Status", "Detail", "Recommendation")
knitr::kable(diagnostic_table, align = c("l", "l", "l", "l"))
```

`r section_heading("Observed and counterfactual outcomes")`

The line extrapolates the fitted pre-event trend. Open points show the
estimated no-event outcomes, and vertical gaps show period-specific effects.

```{r counterfactual}
plot(fit, type = "counterfactual")
```

`r section_heading("Period-specific effects")`

```{r effects}
plot(fit, type = "effects")
```

```{r effects-table}
effect_table <- fit$days
numeric_columns <- vapply(effect_table, is.numeric, logical(1))
effect_table[numeric_columns] <- lapply(
  effect_table[numeric_columns],
  function(x) round(x, 3L)
)
knitr::kable(effect_table, align = "r")
```

`r section_heading("Forecast diagnostics")`

These rolling pre-event forecast errors calibrate the misspecification bound.

```{r diagnostics}
plot(fit, type = "diagnostics")
```

`r section_heading("Survey coverage")`

The line and points show observed period means. The light-gray bars just above
the x-axis show the relative number of responses in each period; the tallest
bar is the period with the most responses.

```{r coverage-plot}
plot(fit, type = "coverage")
```

```{r coverage-table}
coverage <- data.frame(
  Quantity = c(
    "Data level",
    "Input rows",
    "Rows used",
    "Rows omitted for missing outcome or time",
    "Total responses represented",
    "Observed periods",
    "Minimum responses per period",
    "Median responses per period",
    "Maximum responses per period",
    "Missing pre-event periods",
    "Missing forecast periods"
  ),
  Value = c(
    fit$settings$data_level,
    fit$settings$n_input_rows,
    fit$settings$n_used_rows,
    fit$settings$n_omitted_rows,
    fit$settings$total_responses,
    nrow(fit$daily),
    min(fit$daily$n),
    stats::median(fit$daily$n),
    max(fit$daily$n),
    format_periods(fit$settings$missing_pre_periods),
    format_periods(fit$settings$missing_forecast_periods)
  ),
  check.names = FALSE
)
knitr::kable(coverage, align = c("l", "r"))
```

`r section_heading("Analysis settings")`

```{r settings}
settings <- data.frame(
  Setting = c(
    "Formula",
    "Event period",
    "Event-period rule",
    "Report event period",
    "Fit and forecast window",
    "Period schedule",
    "Final fitting span",
    "Final forecast span",
    "Confidence level"
  ),
  Value = c(
    paste(deparse(fit$call$formula, width.cutoff = 500L), collapse = " "),
    as.character(fit$settings$event_time),
    fit$settings$event_day,
    if (fit$settings$event_day == "exclude") {
      "Not applicable (event period excluded)"
    } else if (fit$settings$report_event_day) {
      "Yes"
    } else {
      "No"
    },
    paste(fit$settings$window, "observed periods"),
    fit$settings$schedule,
    paste(fit$settings$fit_span, "periods on the time scale"),
    paste(fit$settings$forecast_span, "periods on the time scale"),
    paste0(format_number(confidence_level, 0), "%")
  ),
  check.names = FALSE
)
knitr::kable(settings, align = c("l", "l"))
```

`r section_heading("Interpretation limits")`

The estimate compares observed outcomes after the event with an extrapolation
of the pre-event trend. A causal interpretation requires that, absent the
event, this trend would have remained a credible short-run counterfactual.
The analysis does not by itself rule out other contemporaneous changes or
event-related changes in who responds to the survey. The honest interval
accounts for sampling uncertainty and the package's bounded forecast
misspecification procedure; it does not make these design assumptions true.

`r if (multiple_analyses) "This analysis is estimated separately from the other analyses in this report; the report does not pool them and does not apply a multiple-comparison adjustment." else "This report concerns one fitted event-survey analysis."`
