---
title: "Understanding Automatic Diagnostics"
description: "Understand each automatic data and design check, and learn what to do when a result needs review."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Understanding Automatic Diagnostics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6.8,
  fig.height = 3.8
)
```

`eventsurvey()` and `eventsurvey_summary()` automatically check features of
the data and design that deserve attention. The checks help users notice
calendar gaps, small period samples, pooled variance substitutions, limited
pre-event information, and windows that cover longer calendar spans than the
requested number of observed periods.

Each check is labeled `OK` or `Review`. A `Review` status is not an error and
does not change the estimate. It asks the analyst to confirm that the data and
design are appropriate for the application.

## The five checks

| Check | `Review` is shown when | Suggested response |
|:--|:--|:--|
| Calendar coverage | One or more calendar periods are unobserved in the analysis span | Confirm that `schedule = "observed"` matches the design, or use `schedule = "consecutive"` when uninterrupted calendar periods are required. Do not create outcomes for dates with no respondents. |
| Responses per period | Any observed period contains fewer than 10 responses | Inspect the affected period means and interpret them cautiously. The threshold is a prompt for review, not a universal minimum sample-size rule. |
| Variance information | A period-specific variance is unavailable | Review the affected periods. The package substitutes the pooled within-period variance for uncertainty calculations; it does not create outcomes. |
| Reference windows | Fewer than five rolling pre-event reference windows are available | Interpret the misspecification bound cautiously and use a longer pre-event series when available. |
| Elapsed window spans | A window containing the requested number of observed periods spans more calendar periods than requested | Decide whether the longer elapsed fitting and forecasting horizons remain substantively comparable. |

## Inspect the diagnostics

Begin with the complete daily schedule in `sample_data`.

```{r setup}
library(eventsurvey)

complete <- sample_data

fit_complete <- eventsurvey(y ~ day, complete)
fit_complete$diagnostics
```

All five checks are `OK` in this example. The same table appears near the top
of the HTML report created by `eventsurvey_report()`.

```{r report, eval = FALSE}
fit_complete |>
  eventsurvey_report("eventsurvey-report.html")
```

## Sparse survey dates

Many surveys do not receive responses every calendar day. Here, several
entire dates are removed from the complete data.

```{r sparse-data}
unobserved_days <- c(-24, -17, -11, -4, 2)
sparse <- subset(complete, !day %in% unobserved_days)

fit_sparse <- eventsurvey(y ~ day, sparse)
fit_sparse$diagnostics
```

```{r sparse-coverage, fig.show = 'hold', out.width = '49%', fig.cap = 'Response counts for complete daily fieldwork (left) and sparse fieldwork (right). Missing dates remain unobserved; the package does not interpolate outcomes.'}
plot(fit_complete, type = "counts")
plot(fit_sparse, type = "counts")
```

The default `schedule = "observed"` forms windows from ordered dates with
responses while retaining their actual time values in estimation. The
calendar-coverage check reports the missing dates. The elapsed-span check
reports that a six-observed-period window may cover more than six calendar
periods. Neither check fills the gaps.

If the design instead requires consecutive calendar periods, request that
restriction explicitly. The sparse example then stops and identifies the
missing periods rather than silently changing the analysis.

```{r consecutive, error = TRUE}
eventsurvey(y ~ day, sparse, schedule = "consecutive")
```

## Small period samples and pooled variance

`eventsurvey_summary()` accepts one row per observed period. A period with a
single respondent has no estimable within-period sample variance, so its
variance can be recorded as `NA`. The package uses the pooled within-period
variance from the remaining periods and flags both the small count and the
substitution.

```{r summary-data}
daily <- aggregate(y ~ day, complete, function(z) {
  c(mean = mean(z), n = length(z), variance = stats::var(z))
})

daily <- data.frame(
  day = daily$day,
  mean = daily$y[, "mean"],
  n = as.integer(daily$y[, "n"]),
  variance = daily$y[, "variance"]
)

daily$n[daily$day == -10] <- 1L
daily$variance[daily$day == -10] <- NA_real_

fit_small_period <- eventsurvey_summary(mean ~ day, daily)
fit_small_period$diagnostics
```

This substitution affects the uncertainty calculation for that period. It
does not replace its observed mean or add respondents.

## Limited pre-event history

Under the default event-period exclusion rule, the estimator needs at least
twice the requested window length plus one observed pre-event period. Meeting
that minimum can leave only one rolling reference window, whereas a longer
pre-event series provides more opportunities to evaluate comparable forecasts.

```{r limited-history}
short_history <- subset(sample_data, day >= -13)

fit_short_history <- eventsurvey(y ~ day, short_history)
fit_short_history$diagnostics
```

The analysis remains estimable, but the `Reference windows` check asks the
analyst to interpret the bias bound cautiously. When additional pre-event
observations genuinely exist, including them provides a stronger diagnostic
record.

## A compact review workflow

The following workflow keeps diagnostics close to the results:

```{r workflow, eval = FALSE}
fit <- eventsurvey(outcome ~ interview_date, survey_data,
  event_time = as.Date("2026-01-15")
)

fit$diagnostics
summary(fit)
plot(fit, type = "counts")
plot(fit, type = "diagnostics")
```

For every `Review` row, document whether the feature reflects the intended
survey schedule and why the resulting comparison remains appropriate. Change
the design only for a substantive reason; the diagnostics do not select a
preferred specification automatically.

## Also see

- [Reading an HTML Report](reading-html-reports.html) to see where diagnostics
  appear alongside the estimates and figures.
- [Methodology and Assumptions](methodology.html) for what the diagnostics can
  and cannot establish.
- [Sparse Survey Schedules](sparse-survey-schedules.html) for complete and
  irregular-fieldwork examples.
