---
title: "Preparing Survey Fieldwork Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Preparing Survey Fieldwork Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`eventsurvey()` expects one respondent per row. Prepare a numeric outcome and
one equally spaced time variable before fitting.

## Dates

```{r}
library(eventsurvey)

dat <- simulate_eventsurvey(seed = 4)
dat$interview_date <- as.Date("2026-06-15") + dat$day
fit <- eventsurvey(y ~ interview_date, dat,
                   event_time = as.Date("2026-06-15"), window = 6)
```

For timestamps, the package converts `POSIXt` values to calendar dates.
Normalize time zones and decide how interviews spanning midnight should be
classified before analysis.

## Outcomes and missingness

Binary variables, numeric scales, and continuous outcomes can be analyzed if
a mean is substantively meaningful. Recode special missing values to `NA`.
Rows with missing outcome or time are omitted with a warning; report that
decision and the resulting daily counts.

## Restricting the analysis span

All pre-event periods from the earliest included period through the day before
the event must be consecutive. If an older part of fieldwork contains gaps,
make the restriction explicit:

```{r}
recent <- subset(dat, day >= -18)
recent_fit <- eventsurvey(y ~ day, recent, event_time = 0, window = 6)
```

Do not remove a date merely because its outcome is unusual. Restrictions
should follow fieldwork operations or a prespecified design rule.
