---
title: "Preparing Survey Fieldwork Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Preparing Survey Fieldwork Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`eventsurvey()` expects one respondent per row. Prepare a numeric outcome and
one equally spaced time variable before fitting.

## Dates

```{r}
library(eventsurvey)

dat <- simulate_eventsurvey(seed = 4)
dat$interview_date <- as.Date("2026-06-15") + dat$day
fit <- eventsurvey(y ~ interview_date, dat,
                   event_time = as.Date("2026-06-15"), window = 6)
```

For timestamps, the package converts `POSIXt` values to calendar dates.
Normalize time zones and decide how interviews spanning midnight should be
classified before analysis.

## Outcomes and missingness

Binary variables, numeric scales, and continuous outcomes can be analyzed if
a mean is substantively meaningful. Recode special missing values to `NA`.
Rows with missing outcome or time are omitted with a warning; report that
decision and the resulting daily counts.

## Sparse and irregular fieldwork

By default, rolling windows contain consecutive *observed survey periods*.
The package detects unobserved dates before and after the event, retains the
actual time values in every trend, and reports both the gaps and each window's
elapsed span. It does not interpolate outcomes for dates with no respondents.

Inspect these diagnostics directly:

```{r}
fit$settings$missing_pre_periods
fit$settings$missing_forecast_periods
fit$settings$fit_span
fit$settings$forecast_span
head(fit$windows)
```

When the design requires uninterrupted calendar days, request strict checking:

```{r}
strict_fit <- eventsurvey(y ~ day, dat, event_time = 0, window = 6,
                          pre_periods = "consecutive")
```

Strict mode stops and lists missing pre-event periods. Do not remove a date
merely because its outcome is unusual. Restrictions should follow fieldwork
operations or a prespecified design rule.

See [Sparse Survey Schedules](sparse-survey-schedules.html) for a complete
simulation comparing uninterrupted and irregular fieldwork, including fitted
counterfactuals and gap diagnostics.
