---
title: "Epifanio, Giani, and Ivandic (2023)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Epifanio, Giani, and Ivandic (2023)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4.2)
```

This article reproduces the `eventsurvey` reanalysis of Epifanio, Giani, and
Ivandic (2023). It estimates short-horizon, calendar-date-specific departures
from an extrapolated no-attack path. These are narrower estimands than the
immediate-, short-, and medium-run interval coefficients in the original
article.

```{r}
library(eventsurvey)
data(published_examples)
epifanio <- subset(published_examples, grepl("Epifanio", study))
privacy <- subset(epifanio, grepl("privacy", outcome))
procedural <- subset(epifanio, grepl("procedural", outcome))
```

The respondent-level replication package is archived with a CC0 declaration
in [Harvard Dataverse](https://doi.org/10.7910/DVN/AUHSMD). The package ships
only the derived daily sufficient statistics used here.

## A transparent treatment of empty dates

The source replication code orders dates with usable responses and forms
rolling windows over those observed dates. The privacy outcome has no usable
response on pre-event days -17 and -12; the procedural outcome has none on day
-17. Thus, the source results are reproduced with
`pre_periods = "observed"`. The safer package default is
`pre_periods = "consecutive"`, which stops when calendar dates are missing.
This article makes the replication choice explicit.

## Privacy-rights restrictions

The privacy analysis uses five observed pre-event periods for fitting and five
forecast periods. Event day is forecast but not reported.

```{r privacy-daily, fig.show='hold', out.width='49%', fig.cap='Daily privacy-rights outcome means and respondent counts. The dashed line marks the July 7 bombings.'}
plot(fit_privacy_preview <- eventsurvey_summary(mean ~ day, privacy,
  n = n, variance = variance, event_time = 0, window = 5,
  report_event_day = FALSE, pre_periods = "observed"), type = "daily") +
  ggplot2::labs(y = "Mean support for privacy restrictions")
plot(fit_privacy_preview, type = "counts")
```

```{r privacy-fit}
fit_privacy <- eventsurvey_summary(mean ~ day, privacy,
  n = n, variance = variance, event_time = 0, window = 5,
  event_day = "include", report_event_day = FALSE,
  pre_periods = "observed"
)
fit_privacy$estimate
```

```{r privacy-table}
privacy_table <- merge(fit_privacy$days, privacy[c("day", "n")],
  by.x = "relative_period", by.y = "day", sort = TRUE)
knitr::kable(privacy_table[c("relative_period", "n", "effect", "conf_low", "conf_high")],
             digits = 3,
             col.names = c("Post day", "Respondents", "Estimate", "95% low", "95% high"))
```

```{r privacy-counterfactual, fig.cap='Observed privacy-rights outcome and the extrapolated no-attack counterfactual.'}
plot(fit_privacy, type = "counterfactual") +
  ggplot2::labs(y = "Mean support for privacy restrictions")
```

```{r privacy-effects, fig.cap='Day-specific privacy-rights effects. Thick gray intervals are 95% honest intervals; thin black intervals are 90% honest intervals.'}
plot(fit_privacy, type = "effects", inner_level = 0.90) +
  ggplot2::labs(y = "Estimated effect on privacy restrictions")
```

## Procedural-rights restrictions

```{r procedural-daily, fig.show='hold', out.width='49%', fig.cap='Daily procedural-rights outcome means and respondent counts. The dashed line marks the July 7 bombings.'}
plot(fit_procedural_preview <- eventsurvey_summary(mean ~ day, procedural,
  n = n, variance = variance, event_time = 0, window = 7,
  report_event_day = FALSE, pre_periods = "observed"), type = "daily") +
  ggplot2::labs(y = "Mean support for procedural restrictions")
plot(fit_procedural_preview, type = "counts")
```

```{r procedural-fit}
fit_procedural <- eventsurvey_summary(mean ~ day, procedural,
  n = n, variance = variance, event_time = 0, window = 7,
  event_day = "include", report_event_day = FALSE,
  pre_periods = "observed"
)
fit_procedural$estimate
```

```{r procedural-table}
procedural_table <- merge(fit_procedural$days, procedural[c("day", "n")],
  by.x = "relative_period", by.y = "day", sort = TRUE)
knitr::kable(procedural_table[c("relative_period", "n", "effect", "conf_low", "conf_high")],
             digits = 3,
             col.names = c("Post day", "Respondents", "Estimate", "95% low", "95% high"))
```

```{r procedural-counterfactual, fig.cap='Observed procedural-rights outcome and the extrapolated no-attack counterfactual.'}
plot(fit_procedural, type = "counterfactual") +
  ggplot2::labs(y = "Mean support for procedural restrictions")
```

```{r procedural-effects, fig.cap='Day-specific procedural-rights effects. Thick gray intervals are 95% honest intervals; thin black intervals are 90% honest intervals.'}
plot(fit_procedural, type = "effects", inner_level = 0.90) +
  ggplot2::labs(y = "Estimated effect on procedural restrictions")
```

All interpretable 95% intervals include zero. For both outcomes, post day 3
contains one response. Its point estimate is shown, but its sampling variance
cannot be estimated separately; the package uses the pooled within-day
variance, so this row is diagnostic and should not support a population-level
conclusion.

## Sensitivity to the window length

The rolling forecast errors underlying the two bias bounds are shown before
the window-length table.

```{r epifanio-diagnostics, fig.show='hold', out.width='49%', fig.cap='Rolling pre-event forecast errors for the privacy-rights and procedural-rights analyses.'}
plot(fit_privacy, type = "diagnostics")
plot(fit_procedural, type = "diagnostics")
```

```{r sensitivity}
fit_grid <- function(data, windows) {
  do.call(rbind, lapply(windows, function(w) {
    fit <- eventsurvey_summary(mean ~ day, data,
      n = n, variance = variance, event_time = 0, window = w,
      report_event_day = FALSE, pre_periods = "observed")
    cbind(window = w, fit$estimate[c("effect", "bias_bound", "conf_low", "conf_high", "n_windows")])
  }))
}
privacy_sensitivity <- fit_grid(privacy, 3:8)
procedural_sensitivity <- fit_grid(procedural, 3:8)
knitr::kable(privacy_sensitivity, digits = 3, caption = "Privacy-rights outcome")
knitr::kable(procedural_sensitivity, digits = 3, caption = "Procedural-rights outcome")
```

## Reference

Epifanio, Mariaelisa, Marco Giani, and Ria Ivandic. 2023. "Wait and See?
Public Opinion Dynamics after Terrorist Attacks." *Journal of Politics* 85(3):
843--859. [Article](https://doi.org/10.1086/723020) ·
[Replication materials](https://doi.org/10.7910/DVN/AUHSMD)
