---
title: "Complete Example Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Complete Example Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4.2)
```

This example follows the recommended sequence: inspect fieldwork, declare the
analysis, fit once, examine diagnostics, and report both the estimate and the
assumptions that support it.

```{r}
library(eventsurvey)

survey_data <- simulate_eventsurvey(seed = 2026, pre = 30, post = 8,
                                    respondents = 40)
```

## Inspect coverage before fitting

```{r coverage}
fit_preview <- eventsurvey(y ~ day, survey_data, event_time = 0, window = 6)
plot(fit_preview, type = "daily")
```

The point size shows the number of respondents in a period. The estimator
requires every calendar period in the analysis span to have at least one
response. This prevents a gap such as Friday-to-Monday from being silently
treated as one period when the estimand is defined by calendar day.

## Prespecify the forecasting operation

We use six days for both fitting and forecasting. With 30 pre-event days, the
package can reproduce this task in `30 - 2 * 6 + 1 = 19` rolling windows, each
with six forecast errors.

```{r}
fit <- eventsurvey(y ~ day, survey_data, event_time = 0, window = 6,
                   alpha = 0.05)
summary(fit)
```

The object keeps inspectable data frames rather than only formatted output:

```{r}
fit$estimate
head(fit$days)
head(fit$reference)
```

## Interpret the two intervals

`conventional_low` and `conventional_high` treat the linear extrapolation as
correct. `conf_low` and `conf_high` are the main honest interval. They combine
sampling uncertainty with the bounded misspecification assumption. The
`bias_bound` is the largest absolute rolling reference error.

```{r counterfactual}
plot(fit)
```

```{r diagnostics}
plot(fit, type = "diagnostics")
```

## Minimum reporting checklist

A transparent analysis should report:

1. the event time and how within-period exposure was classified;
2. the outcome and fieldwork time variable;
3. the fit/forecast window and why it was chosen;
4. coverage and sample sizes across periods;
5. the rolling forecast errors and bias bound;
6. the window-average and period-specific estimates with honest intervals;
7. sensitivity to substantively plausible window lengths; and
8. limitations of event exogeneity and respondent-timing assumptions.
