---
title: "Getting Started"
description: "Fit a first event-survey model, inspect the results, and create a shareable report."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4.2)
```

An event-during-survey design arises when an event occurs while a survey is
already collecting responses. The observed post-event outcome is available,
but its no-event counterpart is not. The central task is therefore to
extrapolate the pre-event path and compare it with what was observed after the
event.

## 1. Prepare respondent-level data

Each row should be a respondent. The outcome must be numeric, and time must be
an integer-like numeric variable, a `Date`, or a `POSIXt`. The package includes
the ready-to-use `sample_data` dataset so the full workflow can be run without
private research data or a separate simulation step.

```{r}
library(eventsurvey)
head(sample_data)
```

In this dataset, `y` is a simulated five-category survey response coded from 1
(lowest) to 5 (highest), and `day` is the interview day relative to the event:
negative values are before the event, 0 is the event day, and positive values
are after the event.
Only these observed variables are included. The no-event counterfactual and
event effects are quantities to be estimated, not columns supplied to
`eventsurvey()`.

## 2. Estimate the effect

The formula contains the outcome and time variables. By default,
`event_time = 0`, `event_day = "exclude"`, and `window = 6`: the model uses the
final six observed pre-event periods, skips the event period, and forecasts
the first six observed post-event periods. The rolling pre-event exercises
reproduce this six-period fit, one-period gap, and six-period forecast to
construct matched forecast errors.

The formula must use exactly two **untransformed column names** in the form
`outcome ~ time`. Thus, `y ~ day` is valid. Formulas such as `log(y) ~ day`,
`y ~ I(day^2)`, `y ~ day + group`, and `y ~ day * group` are rejected because
formula transformations, nonlinear time terms, covariates, and interactions
are not supported by the current methodology. If a substantively meaningful
transformed outcome is needed, create it as a clearly named numeric column
before fitting; the resulting effect is measured in that column's units.

```{r}
fit <- eventsurvey(y ~ day, sample_data)
fit
```

The fitted object automatically checks calendar coverage, responses per
period, variance information, the number of rolling reference windows, and
elapsed fitting and forecasting spans. `summary(fit)` and the HTML report show
each check as `OK` or `Review`. A `Review` flag is descriptive: it does not
change the estimate or automatically invalidate the analysis.
See [Understanding Automatic Diagnostics](automatic-diagnostics.html) for
examples of every check and guidance on responding to a `Review` status.

For a one-command workflow, pipe the fitted analysis to
`eventsurvey_report()`. Without a filename, the package creates a temporary
self-contained HTML report. The default `open = interactive()` opens that
report automatically in an interactive session such as the RStudio console,
but not in `Rscript`, tests, continuous integration, or other batch runs. The
HTML file is created either way. Set `open = TRUE` or `open = FALSE` to
override this behavior.

```{r report-example, eval=FALSE}
eventsurvey(y ~ day, sample_data) |>
  eventsurvey_report()
```

To keep the report, provide an output filename:

```{r report-save-example, eval=FALSE}
eventsurvey(y ~ day, sample_data) |>
  eventsurvey_report("eventsurvey-report.html")
```

The printed interval is the honest bounded-misspecification-error interval.
It is generally wider than the conventional interval because it allows the
post-event extrapolation to be wrong by as much as the worst comparable
pre-event forecast.

## 3. See what was extrapolated

```{r counterfactual}
plot(fit, type = "counterfactual")
```

Dark points are observed daily means. The coral line is the fitted pre-event
trend and its continuation. Open points mark the forecast no-event means;
blue vertical gaps are the day-specific estimates.

```{r effects}
plot(fit, type = "effects")
```

## 4. Inspect the forecasting diagnostic

```{r diagnostics}
plot(fit, type = "diagnostics")
```

Every line is one rolling fit. Its points show forecast errors one through six
periods ahead. These are not placebo treatment effects; they are direct checks
of the same extrapolation task used after the event.

## Event-day conventions

By default, relative period 0 is excluded because respondents interviewed
during the event period often have ambiguous exposure. Forecasting therefore
begins with the first observed period after the event. Include period 0 only
when the event timing and fieldwork make its exposure status defensible.

```{r}
fit_including_event <- eventsurvey(
  y ~ day, sample_data, event_time = 0, window = 6,
  event_day = "include"
)

fit_hidden <- eventsurvey(
  y ~ day, sample_data, event_time = 0, window = 6,
  event_day = "include",
  report_event_day = FALSE
)
```

The second alternative retains the event period in the window-average
estimate but suppresses its day-specific display; use it only when that
estimand is substantively intended. These choices should follow the survey's
fieldwork and event timing, not whichever result is most favorable. Under the
default exclusion rule, the diagnostic also skips one period between each
rolling fit and its forecasts, requiring `2 * window + 1` observed pre-event
periods.

## Also see

- [Preparing Survey Fieldwork Data](data-preparation.html) for variable,
  timing, and data-format requirements.
- [Reading an HTML Report](reading-html-reports.html) for guidance on every
  estimate, diagnostic, and figure in the report.
- [Understanding Automatic Diagnostics](automatic-diagnostics.html) for the
  meaning of each `OK` and `Review` check.
- [Complete Example Workflow](example-workflow.html) for a longer analysis
  with plots and sensitivity checks.
