---
title: "Getting Started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4.2)
```

An event-during-survey design arises when an event occurs while a survey is
already collecting responses. The observed post-event outcome is available,
but its no-event counterpart is not. The central task is therefore to
extrapolate the pre-event path and compare it with what was observed after the
event.

## 1. Prepare respondent-level data

Each row should be a respondent. The outcome must be numeric, and time must be
an integer-like numeric variable, a `Date`, or a `POSIXt`. The package includes
a simulator so the full workflow can be run without private research data.

```{r}
library(eventsurvey)

dat <- simulate_eventsurvey(seed = 10)
head(dat)
```

## 2. Estimate the effect

The formula contains the outcome and time variables. `window = 6` fits a
linear model on the final six pre-event days and forecasts six event/post-event
days. The same six-by-six operation is repeated before the event to construct
matched forecast errors.

```{r}
fit <- eventsurvey(y ~ day, dat, event_time = 0, window = 6)
fit
```

The printed interval is the honest bounded-misspecification-error interval.
It is generally wider than the conventional interval because it allows the
post-event extrapolation to be wrong by as much as the worst comparable
pre-event forecast.

## 3. See what was extrapolated

```{r counterfactual}
plot(fit, type = "counterfactual")
```

Dark points are observed daily means. The coral line is the fitted pre-event
trend and its continuation. Open points mark the forecast no-event means;
teal vertical gaps are the day-specific estimates.

```{r effects}
plot(fit, type = "effects")
```

## 4. Inspect the forecasting diagnostic

```{r diagnostics}
plot(fit, type = "diagnostics")
```

Every line is one rolling fit. Its points show forecast errors one through six
periods ahead. These are not placebo treatment effects; they are direct checks
of the same extrapolation task used after the event.

## Event-day conventions

By default, relative period 0 is included. If respondents interviewed during
the event period had ambiguous exposure, either skip it completely or retain
it in the aggregate estimate while hiding its day-specific result.

```{r}
fit_after <- eventsurvey(
  y ~ day, dat, event_time = 0, window = 6,
  event_day = "exclude"
)

fit_hidden <- eventsurvey(
  y ~ day, dat, event_time = 0, window = 6,
  report_event_day = FALSE
)
```

These choices answer different questions and should be made from the survey's
fieldwork and event timing, not from whichever result is most favorable.
When the event period is excluded, the diagnostic also skips one period between
each rolling fit and its forecasts; this requires `2 * window + 1` pre-event
periods.
