---
title: "Examples"
description: "Explore complete eventsurvey reports using data from two published studies."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

These examples apply the same `eventsurvey` workflow to two published studies.
They are package reanalyses, not reproductions of every model in the original
articles. Each report contains estimates, diagnostics, figures, survey
coverage, and analysis settings.

## Example reports

| Example | Event and outcome | Report |
|:--|:--|:--|
| Bateson and Weintraub (2022) | 2016 U.S. election; trust in the U.S. government | [Open report](https://yhoriuchi.github.io/eventsurvey/reports/bateson-weintraub.html){target="_blank" rel="noopener noreferrer"} |
| Epifanio, Giani, and Ivandic (2023) | 2005 London bombings; privacy- and procedural-rights restrictions | [Open report](https://yhoriuchi.github.io/eventsurvey/reports/epifanio-giani-ivandic.html){target="_blank" rel="noopener noreferrer"} |

## Bateson and Weintraub (2022)

This report presents one seven-period analysis. AmericasBarometer data cannot
be redistributed, so the package includes no respondent records or daily
summaries. Authorized users can obtain the data from
[LAPOP/CGD](https://www.vanderbilt.edu/cgd/data-access/) and regenerate the
report locally.

[Open the Bateson--Weintraub report](https://yhoriuchi.github.io/eventsurvey/reports/bateson-weintraub.html){target="_blank" rel="noopener noreferrer"}

## Epifanio, Giani, and Ivandic (2023)

This report presents separately estimated privacy- and procedural-rights
outcomes. The package includes the period-level sufficient statistics used in
these analyses. Missing survey dates remain unobserved and are not
interpolated.

[Open the Epifanio--Giani--Ivandic report](https://yhoriuchi.github.io/eventsurvey/reports/epifanio-giani-ivandic.html){target="_blank" rel="noopener noreferrer"}

## Reproduce the reports

The rendering script creates both self-contained HTML files. The Bateson
report requires an authorized local source file.

```{r, eval = FALSE}
Sys.setenv(EVENTSURVEY_BATESON_DATA = "/path/to/cleaned_main.csv")
source("data-raw/render-application-reports.R")
```

## References

- Bateson, Regina, and Michael Weintraub. 2022. "The 2016 Election and
  America's Standing Abroad: Quasi-experimental Evidence of a Trump Effect."
  *Journal of Politics* 84(4): 2300--2304.
  [Article](https://doi.org/10.1086/718209) ·
  [Replication materials](https://doi.org/10.7910/DVN/YRJ6E3)

- Epifanio, Mariaelisa, Marco Giani, and Ria Ivandic. 2023. "Wait and See?
  Public Opinion Dynamics after Terrorist Attacks." *Journal of Politics*
  85(3): 843--859.
  [Article](https://doi.org/10.1086/723020) ·
  [Replication materials](https://doi.org/10.7910/DVN/AUHSMD)

## Also see

- [Getting Started](getting-started.html) to fit the package's bundled sample
  data and create a report.
- [Reading an HTML Report](reading-html-reports.html) to interpret the
  estimates, diagnostics, and figures in these examples.
- [Estimating from Period-Level Summary Data](summary-data.html) for analyses
  like the Epifanio--Giani--Ivandic example when respondent records cannot be
  distributed.
- [Complete Example Workflow](example-workflow.html) for an end-to-end
  simulated analysis with sensitivity checks.
