---
title: "Published Applications"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Published Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The website documents two empirical applications used to illustrate
`eventsurvey`. The Epifanio--Giani--Ivandic article runs directly from the
CC0-derived summaries included in the package. The Bateson--Weintraub article
provides an executable local preparation recipe because the AmericasBarometer
license does not permit the package to redistribute its source data.

```{r}
library(eventsurvey)
data(published_examples)
table(published_examples$study, published_examples$outcome)
```

## What can be reproduced

The articles reproduce the **eventsurvey reanalyses** of the published data:
the daily descriptive series, common counterfactual path, day-specific effects,
honest intervals, rolling diagnostics, and window-length sensitivity results.
They do not claim to reproduce every model in the original articles, which use
different estimands and additional specifications.

* [Bateson and Weintraub (2022)](bateson-weintraub.html) studies trust in the
  U.S. government around the 2016 U.S. election.
* [Epifanio, Giani, and Ivandic (2023)](epifanio-giani-ivandic.html) studies
  support for restrictions on privacy and procedural rights after the 2005
  London bombings.

## Data access and redistribution

For the time-only weighted linear model, each date's count, mean, and sample
variance are sufficient for the point estimates and analytic confidence
intervals. The package includes those summaries only where redistribution is
permitted. AmericasBarometer users must obtain data from LAPOP/CGD directly and
agree to its current terms; `eventsurvey` supplies code rather than those data.
The original sources and access conditions remain authoritative.

```{r}
str(published_examples)
```

The summary interface mirrors the respondent-level interface:

```{r, eval = FALSE}
eventsurvey_summary(mean ~ day, application_data,
  n = n, variance = variance, event_time = 0, window = 7
)
```
