---
title: "Reading an HTML Report"
description: "Learn how to interpret each estimate, diagnostic, figure, and setting in the HTML report."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reading an HTML Report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`eventsurvey_report()` collects the estimates, diagnostics, figures, settings,
and reproducibility information for an analysis in one self-contained HTML
file. It does not change or re-estimate the fitted model.

```{r, eval = FALSE}
fit <- eventsurvey(y ~ day, survey_data)
eventsurvey_report(fit)
```

## A useful reading order

Read the report in four steps:

1. Check the **analysis call and settings** to confirm the outcome, time
   variable, event period, event-day rule, window, and schedule.
2. Read the **main result**, especially the estimated average effect and honest
   interval.
3. Review the **automatic diagnostics, forecast diagnostics, and survey
   coverage** before interpreting the estimate.
4. Use the **counterfactual and period-specific figures** to see when and how
   the observed outcomes depart from the extrapolated no-event trend.

## Main result

The average effect is the mean, across the reported event and post-event
periods, of

$$
\text{observed outcome} - \text{estimated no-event outcome}.
$$

A positive estimate means that observed outcomes were higher than the
extrapolated counterfactual; a negative estimate means that they were lower.
The estimate and both intervals remain in the outcome's original units. For
example, an outcome measured on a five-point scale produces effects measured
in scale points.

The table distinguishes two intervals:

- The **conventional interval** reflects sampling uncertainty while treating
  the fitted pre-event trend as correct.
- The **honest interval** adds the bias bound calibrated from matched rolling
  pre-event forecast errors. This is the package's primary interval.

The **bias bound** is the largest absolute matched reference-forecast error.
The counts of **reference windows** and **reference forecasts** show how much
pre-event evidence was available to calibrate that bound.

## Automatic diagnostics

The diagnostic table identifies features that deserve review, including sparse
calendar coverage, small period samples, pooled variance substitution, few
reference windows, or observed-period windows that span more calendar time
than requested. A **Review** status is not a failed test and does not alter the
estimate. It is a prompt to examine the design and report relevant limitations.

See [Understanding Automatic Diagnostics](automatic-diagnostics.html) for the
trigger and recommended response for each check.

## Observed and counterfactual outcomes

The counterfactual figure displays the fitted pre-event trend and extends it
into the event and post-event periods. Filled points are observed period means;
open points are estimated outcomes under no event. Each vertical blue gap is a
period-specific effect.

This figure is most credible when the fitted pre-event trend is locally
reasonable and the post-event departures are not better explained by changing
respondent composition, unrelated contemporaneous events, or fieldwork
changes.

## Period-specific effects

The effects figure and table show how the estimated difference evolves across
periods. The report's main estimate averages these period-specific effects; it
does not imply that the effect is constant over time.

## Forecast diagnostics

The package repeatedly fits the same model in earlier pre-event windows and
forecasts the following observed periods. The resulting errors measure how far
the linear extrapolation missed when no focal event had yet occurred. Large or
systematic errors indicate that the counterfactual trend is difficult to
forecast and widen the honest interval. The blue dashed vertical line and its
`0` label mark the focal event; all reference forecasts appear before it.

## Survey coverage

The combined coverage figure shows observed period means as a line with points.
Light-gray bars just above the x-axis show the relative number of responses in
each period, with the tallest bar marking the period with the most responses.
This makes unusually sparse periods visible without introducing a second axis
or a separate panel. Missing dates remain missing: the report does not
interpolate outcomes for dates with no respondents.

The accompanying table reports the input rows, rows used, rows omitted because
the outcome or time is missing, and the total number of responses represented.
For period-summary input, the total is the sum of the supplied period counts.

## Analysis settings and reproducibility

The settings table records the choices needed to interpret and reproduce the
analysis. The final table records the `eventsurvey` version, R version, and
generation time. Because the output is self-contained, collaborators can open
the HTML file without installing R or the package.

## What the report does not establish

The report organizes evidence; it does not make an event as-if randomized.
Causal interpretation still requires a defensible fieldwork design and the
assumption that, absent the event, the local pre-event trend would have
continued over the short forecast horizon. Diagnostics evaluate forecast
behavior but cannot rule out all contemporaneous changes or shifts in who
responded.

When one report contains several fitted objects, each is estimated separately.
The report does not pool events or outcomes, and it does not automatically
adjust confidence intervals for multiple comparisons.

See [Methodology](methodology.html) for the estimand, extrapolation restriction,
rolling calibration, and identifying assumptions. A link to the working paper
can be added there and on the homepage when it is available.

## Also see

- [Getting Started](getting-started.html) to fit a model and create an HTML
  report.
- [Understanding Automatic Diagnostics](automatic-diagnostics.html) for the
  trigger and recommended response for every diagnostic.
- [Methodology and Assumptions](methodology.html) for the estimand,
  counterfactual restriction, and honest interval.
- [Examples](published-applications.html) to open complete reports using data
  from published studies.
