---
title: "Sensitivity Analysis"
description: "Assess how conclusions change across defensible window lengths and analysis choices."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sensitivity Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The window controls how local the trend is and how far it is extrapolated.
Short windows adapt to local movement but estimate the line from less data;
long windows use more observations but impose linearity over a longer span.

```{r}
library(eventsurvey)

dat <- sample_data
windows <- 3:7
fits <- lapply(windows, function(s) {
  eventsurvey(y ~ day, dat, window = s)
})
sensitivity <- do.call(rbind, lapply(seq_along(fits), function(i) {
  cbind(window = windows[i], fits[[i]]$estimate)
}))
sensitivity[, c("window", "effect", "bias_bound", "conf_low", "conf_high")]
```

Changing the window changes the counterfactual, number of rolling exercises,
bias bound, and sampling uncertainty. Interpret them jointly.

Useful prespecified checks include plausible window lengths, including versus
excluding the event period, restrictions motivated by known fieldwork breaks,
and outcomes or subgroups chosen before inspecting results. Do not select the
window that produces the smallest p-value or narrowest interval.

## Also see

- [Methodology and Assumptions](methodology.html) for how the window defines
  the fitting and forecasting exercise.
- [Getting Started](getting-started.html) for the default analysis and report.
- [Frequently Asked Questions](faq.html) for concise guidance on choosing and
  prespecifying the window.
