---
title: "Sparse Survey Schedules"
description: "See how observed-period and consecutive-calendar schedules behave when fieldwork is sparse."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sparse Survey Schedules}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6.8,
  fig.height = 3.8
)
```

Survey fieldwork often does not produce responses every day. This article
shows how `eventsurvey` handles such schedules without treating an unobserved
date as though it contained an outcome. It compares two versions of the
bundled `sample_data`:

1. a complete schedule with responses every day; and
2. a sparse schedule with several entire survey days removed.

Because the sparse dataset is a subset of the complete dataset, respondents on
the retained dates have exactly the same outcomes in both analyses. The only
difference is the fieldwork schedule.

## Create complete and sparse schedules

```{r setup}
library(eventsurvey)
library(dplyr)

complete <- sample_data

unobserved_days <- c(-24, -17, -11, -4, 2)
sparse <- complete |>
  filter(!day %in% unobserved_days)

fit_complete <- eventsurvey(
  y ~ day,
  complete,
  event_time = 0,
  window = 6
)

fit_sparse <- eventsurvey(
  y ~ day,
  sparse,
  event_time = 0,
  window = 6
)
```

The counts plots make the schedule difference visible. The sparse data have no
responses on four pre-event dates and one post-event date.

```{r coverage, fig.show='hold', out.width='49%', fig.cap='Response counts under complete daily fieldwork (left) and sparse fieldwork (right). The dashed line marks the event date.'}
plot(fit_complete, type = "counts")
plot(fit_sparse, type = "counts")
```

## Inspect what the package detected

The default `schedule = "observed"` uses the requested number of dates with
responses. It does not renumber those dates: their actual time values enter
the trend and forecast calculations. The fitted object records every gap and
the elapsed span of the final windows.

```{r detected-gaps}
fit_sparse$settings$missing_pre_periods
fit_sparse$settings$missing_forecast_periods
fit_sparse$settings$fit_periods
fit_sparse$fitted$relative_period
```

```{r schedule-table, echo = FALSE}
format_periods <- function(x) {
  if (length(x)) paste(x, collapse = ", ") else "None"
}

schedule_summary <- data.frame(
  Schedule = c("Complete", "Sparse"),
  `Missing pre-event periods` = c(
    format_periods(fit_complete$settings$missing_pre_periods),
    format_periods(fit_sparse$settings$missing_pre_periods)
  ),
  `Missing forecast periods` = c(
    format_periods(fit_complete$settings$missing_forecast_periods),
    format_periods(fit_sparse$settings$missing_forecast_periods)
  ),
  `Final fit span` = c(
    fit_complete$settings$fit_span,
    fit_sparse$settings$fit_span
  ),
  `Final forecast span` = c(
    fit_complete$settings$forecast_span,
    fit_sparse$settings$forecast_span
  ),
  `Reference windows` = c(
    fit_complete$estimate$n_windows,
    fit_sparse$estimate$n_windows
  ),
  check.names = FALSE
)

knitr::kable(
  schedule_summary,
  align = c("l", "l", "l", "r", "r", "r"),
  caption = "Detected gaps and elapsed window spans. Spans are measured on the original time scale."
)
```

For the sparse data, the six-period fitting window consists of days
`r paste(fit_sparse$settings$fit_periods, collapse = ", ")`; it spans
`r fit_sparse$settings$fit_span` calendar days. The six-period effect window
uses days `r paste(fit_sparse$fitted$relative_period, collapse = ", ")` and
spans `r fit_sparse$settings$forecast_span` calendar days.

## Compare the fitted counterfactuals

```{r counterfactuals, fig.show='hold', out.width='49%', fig.cap='Observed outcomes and extrapolated no-event counterfactuals under complete daily fieldwork (left) and sparse fieldwork (right). The sparse analysis uses actual calendar dates and leaves unobserved dates empty.'}
plot(fit_complete, type = "counterfactual")
plot(fit_sparse, type = "counterfactual")
```

The two analyses can target different post-event dates, so their estimated
effects and intervals should be compared together with their target windows.

```{r result-table, echo = FALSE}
result_summary <- data.frame(
  Schedule = c("Complete", "Sparse"),
  `Target dates` = c(
    format_periods(fit_complete$fitted$relative_period),
    format_periods(fit_sparse$fitted$relative_period)
  ),
  `Estimated average effect` = c(
    fit_complete$estimate$effect,
    fit_sparse$estimate$effect
  ),
  `Honest CI lower` = c(
    fit_complete$estimate$conf_low,
    fit_sparse$estimate$conf_low
  ),
  `Honest CI upper` = c(
    fit_complete$estimate$conf_high,
    fit_sparse$estimate$conf_high
  ),
  check.names = FALSE
)

knitr::kable(
  result_summary,
  digits = 3,
  align = c("l", "l", "r", "r", "r"),
  caption = "Estimated average effects for each schedule-specific target window."
)
```

These estimates need not be identical. Missing pre-event dates can change the
line used for extrapolation and the reference forecast errors. Missing
post-event dates can also change the estimand because the first six
observed dates are not necessarily the first six calendar dates. The package
therefore reports the targeted dates rather than implying that the two rows
estimate exactly the same quantity.

## Require consecutive calendar days when appropriate

If the research design requires uninterrupted calendar dates, request strict
mode explicitly:

```{r strict-mode, results='hide'}
strict_sparse <- tryCatch(
  eventsurvey(
    y ~ day,
    sparse,
    event_time = 0,
    window = 6,
    schedule = "consecutive"
  ),
  error = conditionMessage
)
```

For the complete data, observed-period and consecutive-period modes give the
same result because no dates are missing. For the sparse data, strict mode
stops and identifies pre-event days -24, -17, -11, and -4 as missing. This
makes the choice explicit:
observed-period mode supports irregular fieldwork, whereas consecutive-period
mode enforces an uninterrupted calendar design.

## Also see

- [Methodology and Assumptions](methodology.html) for the role of the schedule
  in the estimand and rolling forecasts.
- [Understanding Automatic Diagnostics](automatic-diagnostics.html) for the
  coverage and elapsed-span checks produced by sparse schedules.
- [Getting Started](getting-started.html) for the standard estimation and
  reporting workflow.
