---
title: "Estimating from Period-Level Summary Data"
description: "Estimate effects from period-level counts, means, and variances when respondent records are unavailable."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimating from Period-Level Summary Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4.2)
```

`eventsurvey_summary()` is a primary estimation interface for data stored at
the survey-period level. Use it when respondent records cannot be shared, are
unnecessarily large for the task, or have already been reduced to a count,
mean, and sample variance for each observed survey period.

```{r}
library(eventsurvey)
```

## Choose the function that matches the data

| Data available | Function | Required input |
|:--|:--|:--|
| One row per respondent | `eventsurvey()` | Outcome and interview period |
| One row per observed period | `eventsurvey_summary()` | Period mean, count, sample variance, and period |

Both functions use the same time-only linear extrapolation, rolling forecast
diagnostics, bias bound, and interval construction. They return the same
`eventsurvey` object class, so the same `summary()` and `plot()` methods apply.

## Required period-level structure

The summary data must have exactly one row for every observed survey period
and four quantities:

1. The period or interview date.
2. The outcome mean in that period.
3. The number of non-missing outcome observations, `n`.
4. The ordinary within-period sample variance, using denominator `n - 1`.

Do not replace an unobserved date with a fabricated zero-count row or an
interpolated outcome. A date without respondents remains absent. The
`schedule` argument determines whether the analysis treats the observed
periods as the schedule or requires consecutive calendar periods.

## From respondent records to period summaries

The following example first estimates from respondent records and then from
their period-level sufficient statistics.

```{r}
respondents <- sample_data

daily <- aggregate(y ~ day, respondents, function(x) {
  c(mean = mean(x), n = length(x), variance = var(x))
})
daily <- data.frame(
  day = daily$day,
  mean = daily$y[, "mean"],
  n = daily$y[, "n"],
  variance = daily$y[, "variance"]
)

head(daily)
```

The respondent-level call is:

```{r}
fit_respondents <- eventsurvey(
  y ~ day,
  data = respondents
)
```

With the conventional column names `n` and `variance`, the corresponding
period-level call is equally concise:

```{r}
fit_daily <- eventsurvey_summary(
  mean ~ day,
  data = daily
)
```

Use `n = another_count_column` or `variance = another_variance_column` when
the summary columns have different names. Likewise, supply `event_time`
explicitly when the time variable is not coded relative to an event at zero.

For this time-only model, correctly constructed summaries preserve all
information used by the estimator:

```{r}
all.equal(fit_respondents$estimate, fit_daily$estimate)
all.equal(fit_respondents$days, fit_daily$days)
```

## Inspect and plot the result

The result has the same structure and methods as a respondent-level fit.

```{r}
fit_daily
summary(fit_daily)
plot(fit_daily, type = "counterfactual")
plot(fit_daily, type = "effects")
```

## Sparse periods and single responses

The default `schedule = "observed"` supports irregular survey schedules.
The package keeps the actual time values in estimation, reports missing dates,
and reports the elapsed span of the rolling windows. Use
`schedule = "consecutive"` when every calendar period must be observed.

When a period has one response, its sample variance is undefined and may be
recorded as `NA`. The package retains its mean and count and uses the pooled
within-period variance for the sampling-uncertainty calculation. Such a period
should be treated as diagnostically fragile rather than as strong standalone
population evidence.

## Published summary-data example

The bundled `published_examples` object contains daily sufficient statistics
for the Epifanio, Giani, and Ivandic application.

```{r}
data(published_examples)
privacy <- subset(published_examples, grepl("privacy", outcome))

fit_privacy <- eventsurvey_summary(
  mean ~ day,
  data = privacy,
  n = n,
  variance = variance,
  event_time = 0,
  window = 5,
  event_day = "include",
  report_event_day = FALSE,
  schedule = "observed"
)

fit_privacy$estimate
```

This published-application reanalysis explicitly uses
`event_day = "include"` to preserve its established estimand, while suppressing
the ambiguous period-0 day-specific result. New analyses use the safer
`"exclude"` default unless inclusion is substantively justified.

The summary interface protects data access only to the extent that the
released summaries satisfy the relevant license, consent, disclosure, and
privacy requirements. Aggregation does not automatically make restricted data
redistributable.

## Also see

- [Getting Started](getting-started.html) for the respondent-level interface
  and basic reporting workflow.
- [Examples](published-applications.html) for a complete report estimated from
  bundled period-level summaries.
- [Preparing Survey Fieldwork Data](data-preparation.html) for time-variable,
  event-timing, and schedule requirements.
